### 2013-01-08 ISMB/results_ISMB.tex
supp

We present in Fig.~\ref{fig:time} the average times to generate one sequence
with the required \texttt{C+G} content. As expected, the time grows linearly
in function of the length of the structures.  A highly interesting feature
is the huge decrease in time of computation when there is $15\%$ free 
nucleotides inside the loops of the secondary structure.

@@

\subsection{Dataset}
To evaluate the quality of our method, we selected a subset of $50$ secondary
structures from the \textit{RNA STRNAD} database~\cite{andronescu2008rna}.
Those are known secondary structure from a variety of organisms with 
 lengths between $20$ and $100$ nucleotides.

 TODO MORE INFO RNASTRAND???

>>>>

We present the average times spent by \texttt{Incarnation} and \RNAinverse
 to generate one sequence
with the required \texttt{C+G} content in Fig.~\ref{fig:time}. As expected, the time grows linearly
in function of the length of the structures for \texttt{Incarnation}.  A highly interesting feature
is the huge decrease in time of computation when there is $15\%$ free 
nucleotides inside the loops of the secondary structure.

@@

\subsection{Dataset}
To evaluate the quality of our method, we used secondary
structures from the \textit{RNA STRNAD} database~\cite{andronescu2008rna}.
Those are known secondary structure from a variety of organisms.
We select the same subset of $50$ structures as in~\cite{Levin:2012kx}, 
which have lengths between $20$ and $100$ nucleotides.
